Learning to Synthesize Rules for Network Intrusion Detectors

### 2020-02-25 paper/paper.tex
5.1.1

    JBoss JMX\MyComment{ Console Beanshell Exploit} & RCE & HTTP \MyComment{& Remote Code Execution} & \textbf{content}:"/HtmlAdaptor"; nocase; http\_uri; \textbf{content}:"action=inspect"; nocase; http\_uri; \textbf{content}:"bean"; nocase; http\_uri; \textbf{content}:"name="; http\_uri; \\
    WeBid \MyComment{Local File Inclusion} & RFI & TCP \MyComment{& Local File Inclusion} & \textbf{content}:"GET "; depth:4; \textbf{content}:"/cron.php?"; http\_uri; nocase; \textbf{content}:"include\_path="; http\_uri; nocase; \textbf{content}:"../"; \\
    ColdFusion \MyComment{Privilege Escalation} & Privilege Escalation & HTTP \MyComment{& Privilege Escalation} & \textbf{content}:"GET"; http\_method; nocase; \textbf{content}:"/CFIDE/administrator"; http\_uri; nocase; \\
    .htaccess access\MyComment{attempted-recon} & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:".htaccess"; nocase; http\_uri; \\
    .idq access\MyComment{EXPLOIT ISAPI} & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:".idq"; nocase; http\_uri; \\
    iisadmin access\MyComment{web-application-attack} & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:"/iisadmin"; nocase; http\_uri; \\
    /system32/ in URI\MyComment{Possible Protected Directory Access Attempt} & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:"/system32/"; nocase; http\_uri; \\
    Script tag in URI\MyComment{Possible Cross Site Scripting Attempt} & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:"</script>"; nocase; http\_uri; \\
    \bottomrule
  \end{tabular}
\end{table*}

@@

    \midrule
    Ping Scan & 5 & 2 & - \\
    SYN Flood & 2 & 2 & - \\
    JBoss JMX & 23 & 381 & 23 \\
    WeBid & 23 & - & -\\    
    ColdFusion & 19 & 39 & 5\\
    .htaccess access & 17 & 2,458 & 2\\
    .idq access & 19 & 1,111 & 2 \\
    iisadmin access & 17 & 861 & 1 \\
    /system32/ in URI & 20 & 3,665 & 2 \\
    Script tag in URI & 22 & - & - \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\subsubsection{Malicious traffic.}To reproduce the malicious traffic
for http and tcp attacks, we configured an http server (Apache2) in
one machine and Nikto2~\cite{nikto} in a different machine. Nikto is
an open source tool with a catalog of scripts to reproduce
vulnerabilities. It is important to note that this setup is \emph{not}
necessary if \emph{pcap} files---pcap is the input format used by
\tname{}---for the attack already exist. As explained in
Section~\ref{sec:minimization}, pcap files abstract network
messages~\cite{pcap} and can be used to avoid network traffic during
rule synthesis. We proceeded as follows to obtain pcap files for the
the attacks we analyzed: we 1)~instantiated the script (\eg{}, defined
the IP of the web server), 2)~executed the Nikto2 script, 3)~and
monitored the traffic with the Wireshark network
monitor~\cite{wireshark-net-monitor}. The Wireshark tool records the
traffic and reports pcap files on output for replaying. The only
difference in the setup of non-http non-tcp attack is in the first
step of this procedure. For example, we used the hping3~\cite{hping3}
command to reproduce the ICMP SYN Flood attack: \CodeIn{hping3 -d 80
  -w 512 -S -p 80 --flood --rand-source <IP>}. This command alone
reproduces a flooding attack on a given machine
(Section~\ref{sec:dos}).\Mar{what about the variants? where do they
  come from? this is confusing as the narrative above suggests the
  attack is hardcoded in the tool.}

>>>>

    JBoss JMX\MyComment{ Console Beanshell Exploit} & RCE & HTTP \MyComment{& Remote Code Execution} & \textbf{content}:"/HtmlAdaptor"; nocase; http\_uri; \textbf{content}:"action=inspect"; nocase; http\_uri; \textbf{content}:"bean"; nocase; http\_uri; \textbf{content}:"name="; http\_uri; \\
    %% WeBid \MyComment{Local File Inclusion} & RFI & TCP \MyComment{& Local File Inclusion} & \textbf{content}:"GET "; depth:4; \textbf{content}:"/cron.php?"; http\_uri; nocase; \textbf{content}:"include\_path="; http\_uri; nocase; \textbf{content}:"../"; \\
    ColdFusion \MyComment{Privilege Escalation} & Privilege Escalation & HTTP \MyComment{& Privilege Escalation} & \textbf{content}:"GET"; http\_method; nocase; \textbf{content}:"/CFIDE/administrator"; http\_uri; nocase; \\
    .htaccess access\MyComment{attempted-recon} & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:".htaccess"; nocase; http\_uri; \\
    .idq access\MyComment{EXPLOIT ISAPI} & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:".idq"; nocase; http\_uri; \\
    iisadmin access\MyComment{web-application-attack} & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:"/iisadmin"; nocase; http\_uri; \\
    /system32/ in URI\MyComment{Possible Protected Directory Access Attempt} & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:"/system32/"; nocase; http\_uri; \\
    Script tag in URI\MyComment{Possible Cross Site Scripting Attempt} & RCE & HTTP \MyComment{& Adicionar} & \textbf{content}:"</script>"; nocase; http\_uri; \\
    \bottomrule
  \end{tabular}
\end{table*}

@@

    \midrule
    Ping Scan & 5 & 2 & - \\
    SYN Flood & 2 & 2 & - \\
    JBoss JMX & 23 & 381 & 23 \\
    %%   WeBid & 23 & - & -\\    
    ColdFusion & 19 & 39 & 5\\
    .htaccess access & 17 & 2,458 & 2\\
    .idq access & 19 & 1,111 & 2 \\
    iisadmin access & 17 & 861 & 1 \\
    /system32/ in URI & 20 & 3,665 & 2 \\
    Script tag in URI & 22 & - & - \\
    \bottomrule
  \end{tabular}
\end{table}

@@

\subsubsection{Malicious traffic.}To reproduce the malicious traffic
for http and tcp attacks, we configured an http server (Apache2) in
one machine and Nikto2~\cite{nikto} in a different machine. Nikto is
an open source tool with a catalog of scripts to reproduce
vulnerabilities. It is important to note that this setup is \emph{not}
necessary if \emph{pcap} files---pcap is the input format used by
\tname{}---for the attack already exist. As explained in
Section~\ref{sec:minimization}, pcap files abstract network
messages~\cite{pcap} and can be used to avoid network traffic during
rule synthesis. We proceeded as follows to obtain pcap files for the
the attacks we analyzed: we 1)~instantiated the script (\eg{}, defined
the IP of the web server), 2)~executed the Nikto2 script, 3)~and
monitored the traffic with the Wireshark network
monitor~\cite{wireshark-net-monitor}. The Wireshark tool records the
traffic and reports pcap files on output for replaying. The only
difference in the setup of non-http non-tcp attack is in the first
step of this procedure. For example, we used the hping3~\cite{hping3}
command to reproduce the ICMP SYN Flood attack: \CodeIn{hping3 -d 80
  -w 512 -S -p 80 --flood --rand-source <IP>}. This command alone
reproduces a flooding attack on a given machine
(Section~\ref{sec:dos}).\Mar{what about the variants? where do they
  come from? this is confusing as the narrative above suggests the
  attack is hardcoded in the tool.}\Luc{O trafego de um ataque 
  normalmente possui varios pacotes, entre esses varios pacotes alguns 
  deles possuem um padrao. As regras sao criadas descrevendo esse padrao,
  com isso um unico ataque pode disparar varios alertas.

  Porem, existem ataques q so produzem um alerta, ou seja, a regra criada 
  so detecta um dos pacotes do trafego. Nesses casos, procuramos na internet 
  datasets (arquivos pcap) que contivessem mais pacotes desses ataques.
  Fizemos isso tambem para ataques q nos ja tinhamos variacoes, pois
  (teoricamente) quanto mais variacoes, melhor. Existem alguns sites onde 
  eh possivel encontrar pcaps com o trafego de alguns ataques, n consegui
  adicionar nas referencias: 
  https://www.netresec.com/?page=PcapFiles
}
